A general model of microbial interactions in a chemostat

### 2019-12-17 tex/Tracking.tex
delete images

The resulting controls that correct the growth rate can be seen in figures \eqref{Control AOB no noise} and \eqref{Control NOB no noise}. Note that from the structure of a quadratic regulator, since there is no cost in the final state, the end value is always 1. Problem \eqref{Parameter Identification} was solved from the obtained trajectories (figures \eqref{AOB no noise} and \eqref{NOB no noise}) and controls, with no bounds on the parameters. The difference between the control and the fit is expressed in Figure \ref{Difference fit}. Considering that the control is contained in $[0,1]$, the error of fit is below 5 \% almost everywhere through the trajectory.

@@

\clearpage

The original interaction matrix and the fitted interaction matrix can be seen and compared in figure \eqref{Comparison Interaction Matrices}. It can be seen that the new matrix is very different from the original one, in both order of magnitude and sign. Implying that the model is probably not identifiable. The system was simulated again with the new matrix, and one can see that in general terms it captures the outcome of the system as shown in figures \ref{AOB LV simulation}, \ref{NOB LV simulation}, and \ref{Metabolites LV simulation}. The final and central message of this section is that if the interaction function is of the form $1+Ax$, one could be able to get a good fit from the data with the method here presented.

\begin{figure}
	\centering
	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_AOB_Iter_5_LV}
	\caption{AOB trajectories using the identified matrix from figure \eqref{Comparison Interaction Matrices}.}
	\label{AOB LV simulation}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_NOB_Iter_5_LV}
	\caption{NOB trajectories using the identified matrix from figure \eqref{Comparison Interaction Matrices}.}
	\label{NOB LV simulation}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.5 \textwidth]{Synthetic_data_no_noise//221119_no_noise_iter_5_metabolites_Iter_5_LV}
	\caption{Metabolites trajectories using the identified matrix from figure \eqref{Comparison Interaction Matrices}.}
	\label{Metabolites LV simulation}
\end{figure}

@@

Then the procedure from the proof of concept section was applied and one can see that a gLV model is far from describing the pronounced control changes.

\begin{figure}[h]
	\centering
	\includegraphics[width= 0.4\textwidth]{260919_Try1_metabolites_Iter_110_LV}
	\caption{Simulation obtained for the interaction function $I(x) = 1 + Ax$, where $A$ was fitted with the obtained controls from figures \ref{AOB_control} and \ref{NOB_control}.}
	\label{LV_fit}
\end{figure}
\clearpage
\section{Conclusions and Perspectives}

>>>>

The resulting controls that correct the growth rate can be seen in figures \eqref{Control AOB no noise} and \eqref{Control NOB no noise}. Note that from the structure of a quadratic regulator, since there is no cost in the final state, the end value is always 1.

@@

@@

\clearpage
\section{Conclusions and Perspectives}
